Agile Inter-team Software Development

### 2019-01-20 Draft/Parts/Abstract.tex
Changed files to use one line per sentence (better change tracking).
Rewrite abstract.

With the boom in the use of agile process model, imperfect implementations of agile are frequently being seen, out of which the problem of inter-team communication in agile teams is one of the most common issue. An agile team by its definition is a group of people who are self-sufficient to bring their responsibilities to closure, the interaction between different teams is thus considered minimal in most projects implementing agile. This causes problems when the integration of end-products of different teams is carried out. In this paper we have taken a detailed look at this problem and how we can mitigate this.

>>>>

%Problem statement
As the complexity of software development increases, companies relying on agile processes are asked to apply agile at large scale.
However, this conflicts with the basic tenets of agile which focus on interaction and flexibility.
%Proposed Solutions
A typical solution is to run several agile teams in parallel, with appropriate adaptations in process, technology, and architecture.
%Contribution/Method
In this paper, we review the use of agile for large projects, and appropriate adaptations.
